### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex
Added Libo's related work

\section{Empirical}
In this section, we conduct experiments to study the feature selection performances of several well known methods such as Symmetrical Uncertainty Rank, Gain Ratio Rank, Information Gain Rank, Correlation Based Rank, Conditional Entropy Rank \cite{guyon_jmlr03}, Correlation-based Feature Subset Selection \cite{Hall1998},  Reliff \cite{Robnik-Sikonja2003} , mRMR \cite{peng2005} and our proposed methods: High Precision Expectation, High Precision Log likelihood, High Recall Expectation and High Recall Log likelihood. The first five methods are variable rank methods and the last seven are subset rank methods.

>>>>

\section{Empirical}

In this section, we conduct experiments to study the feature selection
performances of several well known methods such as Symmetrical
Uncertainty Rank, Gain Ratio Rank, Information Gain Rank, Correlation
Based Rank, Conditional Entropy Rank \cite{guyon_jmlr03},
Correlation-based Feature Subset Selection \cite{Hall1998}, Reliff
\cite{Robnik-Sikonja2003} , mRMR \cite{peng2005} and our proposed
methods: High Precision Expectation, High Precision Log likelihood,
High Recall Expectation and High Recall Log likelihood. The first five
methods are variable rank methods and the last seven are subset rank
methods.
